### 2024-11-22 paper.tex
first commit

\documentclass[lineno]{jfm}

\usepackage{graphicx}
\usepackage{tikz}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[round]{natbib}
\usepackage{hyperref}
\usepackage{longtable,tabularx}
\usepackage{booktabs}
\hypersetup{
	colorlinks = true,
	urlcolor   = blue,
	citecolor  = black,
}
\usepackage{lipsum}
\usepackage{xcolor}
\usepackage{bm}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

\usepackage{color}
\newcommand{\jl}[1]{{\color{red}#1}}
\newcommand\St{\mbox{\textit{St}}}  % Strouhal number
\newcommand\Ro{\mbox{\textit{Ro}}}  % Strouhal number

\definecolor{green}{rgb}{0.0, 0.5019607843137255, 0.0}
\definecolor{cyan}{rgb}{0.0, 1.0, 1.0}
\definecolor{orange}{rgb}{1.0, 0.6470588235294118, 0.0}
\definecolor{red}{rgb}{1.0, 0.0, 0.0}
\definecolor{purple}{rgb}{0.5019607843137255, 0.0, 0.5019607843137255}
\definecolor{black}{rgb}{0.0,0.0,0.0}
\definecolor{magenta}{rgb}{1.0,0.0,1.0}
\definecolor{blue}{rgb}{0.0,0.0,1.0}

% {\MakeUppercase{\romannumeral #1}}

\title{DNS study of turbulent pipe flow with imposed radial rotation}

\author{Alessandro Ceci\aff{1}
	\corresp{\email{alessandro.ceci@uniroma1.it}} 
	\and Sergio Pirozzoli \aff{1}}

\affiliation{\aff{1} Dipartimento di Ingegneria Meccanica ed Aerospaziale, Sapienza University of Rome, Via Eudossiana 18, 00184 Rome, Italy}

\begin{document}
	\maketitle

	\section{Introduction}\label{sec:intro}

	\section{The numerical dataset} \label{sec:dataset}

	\begin{figure}
		\centering
		\includegraphics[width=0.5\textwidth]{Figures/Pipe_spinning.pdf}
		\caption{
			Definition of coordinate system for DNS of rotating pipe flow.
			$z, r, \theta$ are the axial, radial and azimuthal coordinates, respectively. 
			$R$ is the pipe radius, $L_z$ the pipe
			length, and $u_b$ is the bulk velocity. 
			$\mathbf{\Omega}$ is the angular velocity, and
			$\mathbf{F}_c$ is the resultant mean Coriolis force.
			\textcolor{blue}{The Cartesian coordinates $x_1,x_2$ define positions in the cross-stream plane.}}
			\label{fig:sketch} 
	\end{figure}

	 	\begin{table}
	 	\begin{center}
	 		\def~{\hphantom{0}}  
	 		\begin{tabular}{cccccccc}
	 			\toprule 
	 			$\Rey_b$ & $\Rey_\tau$ & $N$ & $N_z \times N_r \times N_\theta$ & $\lambda \times 10^{-2}$ & Line \\
	 			\midrule
	 			17000 & 508  & 0.0078125 &  $769 \times 97 \times 769$ & 2.862& - \\
	 			17000 & 512  & 0.015625  &  $769 \times 97 \times 769$ & 2.942& - \\
	 			17000 & 523  & 0.03125   &  $769 \times 97 \times 769$ & 3.030& \textcolor{green}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 538  & 0.0625    &  $769 \times 97 \times 769$ & 3.212& \textcolor{cyan}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 566  & 0.125     &  $769 \times 97 \times 769$ & 3.553& \textcolor{orange}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 610  & 0.25      &  $769 \times 97 \times 769$ & 4.120& \textcolor{red}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 642  & 0.375     &  $769 \times 97 \times 769$ & 4.576& \textcolor{purple}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 669  & 0.5       &  $769 \times 97 \times 769$ & 4.962& \textcolor{black}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 748  & 1.0       &  $769 \times 97 \times 769$ & 6.208& \textcolor{magenta}{\rule{0.05\linewidth}{0.75mm}} \\
	 			17000 & 856  & 2.0       &  $769 \times 97 \times 769$ & 8.117& \textcolor{blue}{\rule{0.05\linewidth}{0.75mm}} \\

	 			\midrule
	 			44000  & 1405  & 0.5  & $1793 \times 165 \times 1793$ & 3.262& -\\
	 			\midrule
	 			82500  & 2379  & 0.5  & $3073 \times 244 \times 3073$ & 2.662& -\\
	 			\midrule
	 			133000 & 3634  & 0.5  & $4609 \times 328 \times 4609$ & 2.389& \textcolor{black}{\rule{0.05\linewidth}{0.75mm}}\\
	 			\bottomrule
	 		\end{tabular}
	 		\caption{Flow parameters for DNS of rotating pipe flow.
	 			The bulk Reynolds number defined as $\Rey_b = 2 R u_b/\nu$, with $R$ 
	 			the pipe radius, $u_b$ the bulk velocity and 
	 			$\nu$ the fluid kinematic viscosity.
	 			$N = \Omega R/u_b$ is the rotation number 
	 			and $N_\tau = \Omega R/u^*_{\tau}$ is the friction rotation number
	 			with the global frcition velocity.
	 			$N_z, N_r, N_\theta$ are respectively the number of grid points in the axial,
	 			radial and azimuthal direction.
	 			The global friction factor is $\lambda = 8 \tau_w^* / \rho u_b^2$, with
	 			$\tau_w^*$ the azimuthally averaged mean wall shear stress and $\rho$ the fluid density.
	 			$\Rey_{\tau} = R u^*_{\tau} / \nu$ is the friction Reynolds number,
	 			with $u^*_{\tau} = \sqrt{(\tau_w^*/\rho)}$ the mean friction velocity.
	 		} 
	 		\label{tab:runs} 
	 		\end{center}
 		\end{table}

	\section{Flow organisation} \label{sec:flow}

	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0_u.png}  
		(b) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.00390625_u.png}  
		(c) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0078125_u.png} 
		(d) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.015625_u.png}   
		(e) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.03125_u.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0625_u.png} 
		(g) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.125_u.png}  
		(h) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.1875_u.png}  
		(i) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.25_u.png}
		(j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty1.0_u.png} 
    		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous axial velocity contours at $\Rey_b = 17000$
			in the cross-stream plane.
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
		    }
			\label{fig:urt_500} 
	\end{figure}
	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0_T.png}  
		(b) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.00390625_T.png}  
		(c) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0078125_T.png} 
		(d) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.015625_T.png} 
		(e) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.03125_T.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.0625_T.png} 
		(g) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.125_T.png}  
		(h) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.1875_T.png} 
		(i) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.25_T.png} 
                (j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty1.0_T.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous temperature contours at $\Rey_b = 17000$
			in the cross-stream plane.
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
		}
		\label{fig:trt_500} 
	\end{figure}

%	\begin{figure}
%		\centering
%		(a) \includegraphics[width=4.cm]{Figures/front_a0p005_ret3000_trim.pdf}  
%		(b) \includegraphics[width=4.cm]{Figures/front_a0p25_ret3000_trim.pdf} 
%		(c) \includegraphics[width=4.cm]{Figures/front_a8p0_ret3000_trim.pdf} \\ 
%		\includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
%		\caption{
%			Instantaneous axial velocity contours at $\Rey_b = 133000$
%			in the cross-stream plane.
%			Contour levels ranging from 0 to 1.4 are shown,
%			in colour scale from blue to red. 
%			The pressure side of the pipe is on the left, and the suction side is on the right
%			of each sub-panel.
%			Various rotation numbers are considered:
%			(a) $N = 0.01$,
%			(b) $N = 0.5$,
%			(c) $N = 16.0$.
%		    }
%			\label{fig:urt_3000} 
%	\end{figure}

	\begin{figure}
		\centering
		(a) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0_u.png}  
                (b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.00390625_T.png} \\
		(b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0078125_u.png}  
		(c) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.015625_u.png} \\
		(d) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.03125_u.png} 
                (e) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0625_u.png} \\
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.125_u.png} 
                (g) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.1875_u.png} \\ 
		(h) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.25_u.png} 
		(i) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.5_u.png} \\
                (j) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty1.0_u.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous axial velocity ($u_z/u_b$) contours at $\Rey_b = 17000$
			in an unrolled cylindrical shell at a distance
			$y^*=15$ from the wall (evaluated in the non-rotating case).
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The insets in the top-right corner of each panel report magnified views of a small portion of the shell.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$,
                        (g) $N = 0.1875$,
                        (h) $N = 0.25$,
                        (i) $N = 0.5$,
                        (j) $N = 2.0$.
		}
			\label{fig:utz_500} 
	\end{figure}

	\begin{figure}
		\centering
                (a) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0_T.png}
                (b) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.00390625_T.png} \\
                (c) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0078125_T.png} 
                (d) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.015625_T.png} \\
                (e) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.03125_T.png} 
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.0625_T.png} \\
                (f) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.125_T.png} 
                (g) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.1875_T.png} \\ 
                (h) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.25_T.png} 
                (i) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty0.5_T.png} \\
                jj) \includegraphics[width=6.cm]{Figures/unrolled_rotz0_roty1.0_T.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uz_cmap.eps}
		\caption{
			Instantaneous temperature ($t_z/t_b$) at $\Rey_b = 17000$
			in an unrolled cylindrical shell at a distance
			$y^*=15$ from the wall (evaluated in the non-rotating case).
			Contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The insets in the top-right corner of each panel report magnified views of a small portion of the shell.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
			(b) $N = 0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$,
			(g) $N = 0.1875$,
                        (h) $N = 0.25$,
                        (i) $N = 0.5$,
                        (j) $N = 2.0$.
		    }
			\label{fig:ttz_3000} 
	\end{figure}

	\begin{figure}
		\centering
		(a) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0_u.png}  
		(b) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.00390625_u.png}  
		(c) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0078125_u.png} 
		(d) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.015625_u.png} 
		(e) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.03125_u.png} \\ 
		(f) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0625_u.png} 
		(g) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.125_u.png}  
		(h) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.1875_u.png} 
		(i) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.25_u.png} 
                (j) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.5_u.png} \\
		(k) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty1.0_u.png} 
		\\ \includegraphics[width=0.5\textwidth]{Figures/uzmean_cmap.eps}
		\caption{
			Mean axial velocity contours with 
			superposed cross-flow streamlines, at $\Rey_b = 17000$.
			Twenty-four contour levels ranging from 0 to 1.4 are shown,
			in colour scale from blue to red. 
			The pressure side of the pipe is on the left, and the suction side is on the right
			of each sub-panel.
			Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
                        (g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.	
		    }
			\label{fig:Urt_500} 
	\end{figure}

	\begin{figure}
                \centering
                (a) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0_T.png}
                (b) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.00390625_T.png}
                (c) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0078125_T.png}
                (d) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.015625_T.png}
                (e) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.03125_T.png} \\
                (f) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.0625_T.png}
                (g) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.125_T.png}
                (h) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.1875_T.png}
                (i) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.25_T.png}
                (j) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty0.5_T.png}
                (k) \includegraphics[width=2.cm]{Figures/meanfield_rotz0_roty1.0_T.png}
                \\ \includegraphics[width=0.5\textwidth]{Figures/uzmean_cmap.eps}
                \caption{
                        Mean temperature contours with
                        superposed cross-flow streamlines, at $\Rey_b = 17000$.
                        Twenty-four contour levels ranging from 0 to 1.4 are shown,
                        in colour scale from blue to red.
                        The pressure side of the pipe is on the left, and the suction side is on the right
                        of each sub-panel.
                        Various rotation numbers are considered:
                        (a) $N = 0.0$,
                        (b) $N = 0.0.078125$,
                        (c) $N = 0.015625$,
                        (d) $N = 0.0315$,
                        (e) $N = 0.0625$,
                        (f) $N = 0.125$
			(g) $N = 0.25$,
                        (h) $N = 0.375$,
                        (i) $N = 0.5$,
			(j) $N = 1.0$,
                        (k) $N = 2.0$.
                    }
                        \label{fig:Trt_500}
        \end{figure}

%	\begin{figure}
%		\centering
%		(a)
%		\includegraphics[width=3.cm]{Figures/meanupsi_RETAU3000_ROTATING_Y_A0p005_CORIOLIS.eps}   
%		(b)
%		\includegraphics[width=3.cm]{Figures/meanupsi_RETAU3000_ROTATING_Y_A0p25_CORIOLIS.eps} 
%		(c)
%		\includegraphics[width=3.cm]{Figures/meanupsi_RETAU3000_ROTATING_Y_A8p0_CORIOLIS.eps}  
%    		\\ \includegraphics[width=0.5\textwidth]{Figures/uzmean_cmap.eps}
%		\caption{
%			Mean axial velocity contours with 
%			superposed cross-flow streamlines, at $\Rey_b = 133000$.
%			Twenty-four contour levels ranging from 0 to 1.4 are shown,
%			in colour scale from blue to red. 
%			The pressure side of the pipe is on the left, and the suction side is on the right
%			of each sub-panel.
%			Various rotation numbers are considered:
%			(a) $N = 0.01$,
%			(b) $N = 0.5$,
%			(c) $N = 16.0$.
%		    }
%			\label{fig:Urt_3000} 
%	\end{figure}

%	\begin{figure}
%		\centering
%		(a) \includegraphics[width=5.25cm]{Figures/cf_azimuth_500.eps}   
%		(b) \includegraphics[width=5.25cm]{Figures/cf_azimuth_norm_500.eps} \\
%		(c) \includegraphics[width=5.25cm]{Figures/cf_azimuth_3000.eps}   
%		(d) \includegraphics[width=5.25cm]{Figures/cf_azimuth_norm_3000.eps} \\
%		\caption{
%			Polar distribution of the \textcolor{blue}{local streamwise wall shear stress} ($\tau_w$),
%	                normalised by either the reference dynamic pressure $\rho u_b ^2$ (a, c),
%                 	or the mean wall shear stress $\tau_w^*$ (b, d), at 
%			$\Rey_b=17000$ (a, b), and $\Rey_b=133000$ (c, d).
%			The color codes correspond to different values of $N$, 
%			as given in table~\ref{tab:runs},
%			gray denoting cases without rotation.
%			The dashed blue line in panels (a, c)
%			denotes the predictive formula given in equation~\eqref{eq:fric_polar}.
%			}
%			\label{fig:Cf_polar} 
%	\end{figure}

	\begin{figure}
		\centering
		(a) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.00390625.eps}
                (b) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.0078125.eps} \\
                (c) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.015625.eps}
                (d) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.03125.eps} \\
                (e) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.0625.eps} 
                (f) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.125.eps} \\
                (g) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.1875.eps}
                (h) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.25.eps} \\
                (i) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty0.5.eps}
		(j) \includegraphics[width=4cm]{Figures/prof_uzub_rotz0_roty1.0.eps} \\ 
    		\includegraphics[width=0.5\textwidth]{Figures/theta_cmap_half.eps}
     		\caption{
    		Radial profiles of 
    		outer-scaled axial velocity 
    		at various azimuthal positions, 
		for flow cases at $\Rey_b=17000$.
		Only the interval $\theta = [0^{\circ},90^{\circ}]$ is shown, at stations
		spaced $7.5^\circ$ apart, with negative values of $r$ signifying profiles
		taken at $\theta + 180^{\circ}$.
                (a) $N = 0.0.078125$,
                (b) $N = 0.015625$,
                (c) $N = 0.0315$,
                (d) $N = 0.0625$,
                (e) $N = 0.125$
                (f) $N = 0.25$,
                (g) $N = 0.375$,
                (h) $N = 0.5$,
                (i) $N = 1.0$,
                (j) $N = 2.0$.
		The black solid line denotes the mean axial velocity profile in the
    		non-rotating case.
    	}
	\label{fig:uprof}
	\end{figure}

        \begin{figure}
                \centering
		(a) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.00390625.eps} 
		(b) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.0078125.eps} \\
		(c) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.015625.eps}
		(d) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.03125.eps} \\
                (e) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.0625.eps} 
                (f) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.125.eps} \\
                (g) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.1875.eps}
                (h) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.25.eps} \\
                (i) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty0.5.eps}
                (j) \includegraphics[width=4cm]{Figures/prof_tttb_rotz0_roty1.0.eps} \\
                \includegraphics[width=0.5\textwidth]{Figures/theta_cmap_half.eps}
                \caption{
                Radial profiles of
                outer-scaled temperature
                at various azimuthal positions,
                for flow cases at $\Rey_b=17000$.
                Only the interval $\theta = [0^{\circ},90^{\circ}]$ is shown, at stations
                spaced $7.5^\circ$ apart, with negative values of $r$ signifying profiles
                taken at $\theta + 180^{\circ}$.
                (a) $N = 0.0.078125$,
                (b) $N = 0.015625$,
                (c) $N = 0.0315$,
                (d) $N = 0.0625$,
                (e) $N = 0.125$
                (f) $N = 0.25$,
                (g) $N = 0.375$,
                (h) $N = 0.5$,
                (i) $N = 1.0$,
                (j) $N = 2.0$.
                The black solid line denotes the mean axial velocity profile in the
                non-rotating case.
        }
        \label{fig:tprof}
        \end{figure}

        \begin{figure}
    	\centering
		(a) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.00390625.eps}
                (b) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.0078125.eps} \\
                (c) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.015625.eps}
                (d) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.03125.eps} \\
                (e) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.0625.eps}
                (f) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.125.eps} \\
                (g) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.1875.eps}
                (h) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.25.eps} \\
                (i) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty0.5.eps}
                (j) \includegraphics[width=4cm]{Figures/prof_uzplus_rotz0_roty1.0.eps} \\
	    	\includegraphics[width=0.5\textwidth]{Figures/theta_cmap.eps}
    	\caption{
    		Wall-normal profiles of 
    		inner-scaled axial velocity,
    		at various azimuthal positions spaced 
		$7.5^\circ$ apart,
		for flow cases at $\Rey_b=17000$.
		Only the interval $\theta = [0^{\circ},180^{\circ}]$ is shown.
    	        (a) $N = 0.0.078125$,
                (b) $N = 0.015625$,
                (c) $N = 0.0315$,
                (d) $N = 0.0625$,
                (e) $N = 0.125$
                (f) $N = 0.25$,
                (g) $N = 0.375$,
                (h) $N = 0.5$,
                (i) $N = 1.0$,
                (j) $N = 2.0$.	
    		The black solid line denotes the mean axial velocity profile in the
    		non-rotating case.
    		The dashed gray lines depict the compound law-of-the wall
    		$U^+=y^+$, $U^+=\log y^+/0.387 + 4.53$.
    	}
		\label{fig:uplus}
	\end{figure}

        \begin{figure}
        \centering
                (a) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.00390625.eps}
                (b) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.0078125.eps} \\
                (c) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.015625.eps}
                (d) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.03125.eps} \\
                (e) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.0625.eps}
                (f) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.125.eps} \\
                (g) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.1875.eps}
                (h) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.25.eps} \\
                (i) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty0.5.eps}
                (j) \includegraphics[width=4cm]{Figures/prof_ttplus_rotz0_roty1.0.eps} \\
                \includegraphics[width=0.5\textwidth]{Figures/theta_cmap.eps}
        \caption{
                Wall-normal profiles of
                inner-scaled temperature,
                at various azimuthal positions spaced
                $7.5^\circ$ apart,
                for flow cases at $\Rey_b=17000$.
                Only the interval $\theta = [0^{\circ},180^{\circ}]$ is shown.
                (a) $N = 0.0.078125$,
                (b) $N = 0.015625$,
                (c) $N = 0.0315$,
                (d) $N = 0.0625$,
                (e) $N = 0.125$
                (f) $N = 0.25$,
                (g) $N = 0.375$,
                (h) $N = 0.5$,
                (i) $N = 1.0$,
                (j) $N = 2.0$.
                The black solid line denotes the mean temperature profile in the
                non-rotating case.
                The dashed gray lines depict the compound law-of-the wall
		$\theta^{+}=y^+$, $\theta^{+}=\log y^+/0.387 + 4.53$.
        }
                \label{fig:tplus}
        \end{figure}

        \begin{figure}
        \centering
                (a) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.00390625.eps}
                (b) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.0078125.eps} \\
                (c) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.015625.eps}
                (d) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.03125.eps} \\
                (e) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.0625.eps}
                (f) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.125.eps} \\
                (g) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.1875.eps}
                (h) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.25.eps} \\
                (i) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty0.5.eps}
                (j) \includegraphics[width=4cm]{Figures/prof_uzstar_rotz0_roty1.0.eps} \\
                \includegraphics[width=0.5\textwidth]{Figures/theta_cmap.eps}
        \caption{
                Wall-normal profiles of
                outer-scaled axial velocity,
                at various azimuthal positions spaced
                $7.5^\circ$ apart,
                for flow cases at $\Rey_b=17000$.
                Only the interval $\theta = [0^{\circ},180^{\circ}]$ is shown.
                (a) $N = 0.0.078125$,
                (b) $N = 0.015625$,
                (c) $N = 0.0315$,
                (d) $N = 0.0625$,
                (e) $N = 0.125$
                (f) $N = 0.25$,
                (g) $N = 0.375$,
                (h) $N = 0.5$,
                (i) $N = 1.0$,
                (j) $N = 2.0$.
                The black solid line denotes the mean axial velocity profile in the
                non-rotating case.
                The dashed gray lines depict the compound law-of-the wall
                $U^+=y^+$, $U^+=\log y^+/0.387 + 4.53$.
        }
                \label{fig:ustar}
        \end{figure}

	\begin{figure}
        \centering
                (a) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.00390625.eps}
                (b) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.0078125.eps} \\
                (c) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.015625.eps}
                (d) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.03125.eps} \\
                (e) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.0625.eps}
                (f) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.125.eps} \\
                (g) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.1875.eps}
                (h) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.25.eps} \\
                (i) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty0.5.eps}
                (j) \includegraphics[width=4cm]{Figures/prof_ttstar_rotz0_roty1.0.eps} \\
                \includegraphics[width=0.5\textwidth]{Figures/theta_cmap.eps}
        \caption{
                Wall-normal profiles of
                outer-scaled temperature,
                at various azimuthal positions spaced
                $7.5^\circ$ apart,
                for flow cases at $\Rey_b=17000$.
                Only the interval $\theta = [0^{\circ},180^{\circ}]$ is shown.
                (a) $N = 0.0.078125$,
                (b) $N = 0.015625$,
                (c) $N = 0.0315$,
                (d) $N = 0.0625$,
                (e) $N = 0.125$
                (f) $N = 0.25$,
                (g) $N = 0.375$,
                (h) $N = 0.5$,
                (i) $N = 1.0$,
                (j) $N = 2.0$.
                The black solid line denotes the mean temperature profile in the
                non-rotating case.
                The dashed gray lines depict the compound law-of-the wall
		$\theta^{+}=y^+$, $\theta^{+}=\log y^+/0.387 + 4.53$.
        }
                \label{fig:tstar}
        \end{figure}

       \begin{figure}
       \centering
 	       (a) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.00390625.eps}
               (b) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.0078125.eps} \\
               (c) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.015625.eps}
               (d) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.03125.eps} \\
               (e) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.0625.eps}
               (f) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.125.eps} \\
               (g) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.1875.eps}
               (h) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.25.eps} \\
               (i) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty0.5.eps}
               (j) \includegraphics[width=4cm]{Figures/prof_tkeouter_rotz0_roty1.0.eps} \\
               \includegraphics[width=0.5\textwidth]{Figures/theta_cmap_half.eps} \\
       \caption{
               Radial profiles of 
               outer-scaled turbulence kinetic energy
               at various azimuthal positions, 
               for flow cases at $\Rey_b=17000$.
               Only the interval $\theta = [0^{\circ},90^{\circ}]$ is shown, at stations
               spaced $7.5^\circ$ apart, with negative values of $r$ signifying profiles
               taken at $\theta + 180^{\circ}$.
               (a) $N = 0.03125$,
               (b) $N = 0.5$,
               (c) $N = 2.0$,
               (d) $N = 8.0$.
               (e) $N = 0.1$,
               (f) $N = 0.5$,
               (g) $N = 2.0$,
               (h) $N = 16.0$.
               The black solid line denotes the mean turbulence kinetic energy profile in the
               non-rotating case.
               }
               \label{fig:tke}
       \end{figure}

       \begin{figure}
       \centering
               (a) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.00390625.eps}
               (b) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.0078125.eps} \\
               (c) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.015625.eps}
               (d) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.03125.eps} \\
               (e) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.0625.eps}
               (f) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.125.eps} \\
               (g) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.1875.eps}
               (h) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.25.eps} \\
               (i) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty0.5.eps}
               (j) \includegraphics[width=4cm]{Figures/prof_rssouter_rotz0_roty1.0.eps} \\
               \includegraphics[width=0.5\textwidth]{Figures/theta_cmap_half.eps} \\
       \caption{
               Radial profiles of
               outer-scaled Reynolds shear stress
               at various azimuthal positions,
               for flow cases at $\Rey_b=17000$.
               Only the interval $\theta = [0^{\circ},90^{\circ}]$ is shown, at stations
               spaced $7.5^\circ$ apart, with negative values of $r$ signifying profiles
               taken at $\theta + 180^{\circ}$.
               (a) $N = 0.03125$,
               (b) $N = 0.5$,
               (c) $N = 2.0$,
               (d) $N = 8.0$.
               (e) $N = 0.1$,
               (f) $N = 0.5$,
               (g) $N = 2.0$,
               (h) $N = 16.0$.
               The black solid line denotes the Reynolds shear stress profile in the
               non-rotating case.
               }
               \label{fig:rss}
       \end{figure}

%	\begin{figure}
%		\centering
%		(a)
%		\includegraphics[width=5.25cm]{Figures/scaling_uzplus_500.eps}
%		(b)
%		\includegraphics[width=5.25cm]{Figures/scaling_uzplus_3000.eps}
%		\\
%		\caption{
%			Inner-scaled wall-normal mean velocity profiles at $\theta = 180^\circ$ (pressure side).
%			Solid lines refer to DNS data and dashed lines to equation~\eqref{eq:yang}, for flow
%			cases at $\Rey_b = 17000$ (a) and cases at $\Rey_b = 133000$ (b).
%			Color codes are as in table~\ref{tab:runs}.
%		    }
%		\label{fig:yang}
%	\end{figure}
%
%
%	\begin{figure}
%    	\centering
%		\begin{tabular}{llll}
%			\includegraphics[width=3.0cm]{Figures/tke_RETAU500_ROTATING_Y_A0p015625_CORIOLIS.eps}  &
%			\includegraphics[width=3.0cm]{Figures/tke_RETAU500_ROTATING_Y_A0p25_CORIOLIS.eps}  &
%			\includegraphics[width=3.0cm]{Figures/tke_RETAU500_ROTATING_Y_A1p0_CORIOLIS.eps}  &
%		\includegraphics[width=3.0cm]{Figures/tke_RETAU500_ROTATING_Y_A4p0_CORIOLIS.eps} \\
%			(a) & (b) & (c) & (d) \\
%			\includegraphics[width=3.0cm]{Figures/tke_RETAU3000_ROTATING_Y_A0p05_CORIOLIS.eps}  &
%			\includegraphics[width=3.0cm]{Figures/tke_RETAU3000_ROTATING_Y_A0p25_CORIOLIS.eps}  &
%			\includegraphics[width=3.0cm]{Figures/tke_RETAU3000_ROTATING_Y_A1p0_CORIOLIS.eps}  &
%		\includegraphics[width=3.0cm]{Figures/tke_RETAU3000_ROTATING_Y_A8p0_CORIOLIS.eps} \\
%			(e) & (f) & (g) & (h) \\
%		\end{tabular}
%		\\
%		\includegraphics[width=0.5\textwidth]{Figures/theta_cmap_half.eps} \\
%    	\caption{
%    		Radial profiles of 
%    		outer-scaled turbulence kinetic energy
%    		at various azimuthal positions, 
%		for flow cases at $\Rey_b=17000$ (a-d), and $\Rey_b=133000$ (e-h).
%		Only the interval $\theta = [0^{\circ},90^{\circ}]$ is shown, at stations
%		spaced $7.5^\circ$ apart, with negative values of $r$ signifying profiles
%		taken at $\theta + 180^{\circ}$.
%    		(a) $N = 0.03125$,
%    		(b) $N = 0.5$,
%    		(c) $N = 2.0$,
%    		(d) $N = 8.0$.
%		(e) $N = 0.1$,
%		(f) $N = 0.5$,
%		(g) $N = 2.0$,
%		(h) $N = 16.0$.
%    		The black solid line denotes the mean turbulence kinetic energy profile in the
%    		non-rotating case.
%		}
%		\label{fig:tke}
%	\end{figure}
%	 
%	\begin{figure}
%    	\centering
%		\begin{tabular}{lll}
%		\includegraphics[width=4.cm]{Figures/ekman_uz_utheta_500.eps} &
%		\includegraphics[width=4.cm]{Figures/ekman_angle_500.eps} &
%		\includegraphics[width=4.cm]{Figures/ekman_spiral_500.eps} \\
%		(a) & (b) & (c) \\	
%		\end{tabular}
%    	\caption{
%    		Profiles of 
%		mean axial ($U_z$) and azimuthal ($U_\theta$) velocity
%		(a), wall-parallel flow angle $\varphi = \tan^{-1} (U_{\theta}/U_z)$ (b) 
%		and hodograph diagram (c) 
%		at the polar coordinate $\theta = \pi/2$ (north pole of the pipe).
%		Data are shown for $\Rey_b=17000$, at various rotation numbers:
%    		$N = 0.03125$,
%    		$N = 0.0625$,
%    		$N = 0.125$,
%    		$N = 0.25$,
%    		$N = 0.5$,
%    		$N = 2.0$,
%    		$N = 4.0$,
%    		$N = 8.0$,
%		see table~\ref{tab:runs} for the color codes.
%    		The velocity profiles are scaled by the 
%    		mean centreline axial velocity $U_{0}$.
%    		The black circles denote the analytical solution 
%		for a laminar Ekman layer~\citep{greenspan1968}.
%    	}
%		\label{fig:Ekman_500}
%	\end{figure}
%	 
%	\begin{figure}
%		\centering
%		\begin{tabular}{lll}
%		\includegraphics[width=4.cm]{Figures/ekman_uz_utheta_3000.eps} &
%		\includegraphics[width=4.cm]{Figures/ekman_angle_3000.eps} &
%		\includegraphics[width=4.cm]{Figures/ekman_spiral_3000.eps} \\
%		(a) & (b) & (c) \\
%		\end{tabular}
%    	\caption{
%    		Profiles of 
%		mean axial ($U_z$) and azimuthal ($U_\theta$) velocity
%		(a), wall-parallel flow angle $\varphi = \tan^{-1} (U_{\theta}/U_z)$ (b) 
%		and hodograph diagram (c) 
%		at the polar coordinate $\theta = \pi/2$ (north pole of the pipe).
%		Data are shown for $\Rey_b=133000$, at various rotation numbers:
%			$N = 0.1$,
%			$N = 0.5$,
%			$N = 2.0$,
%			$N = 16.0$,
%		see table~\ref{tab:runs} for the color codes.
%    		The velocity profiles are scaled by the 
%    		mean centreline axial velocity $U_{0}$.
%    		The black circles denote the analytical solution 
%		for a laminar Ekman layer~\citep{greenspan1968}.
%		}
%		\label{fig:Ekman_3000}
%	\end{figure}
%	 
%	\section{Friction} \label{sec:friction}
%
%	\begin{figure}
%		\centering
%		\begin{tabular}{ll}
%		\includegraphics[width=5.0cm]{Figures/scatter_500.eps} &
%		\includegraphics[width=5.0cm]{Figures/scatter_3000.eps} \\
%		(a) & (b)
%		\end{tabular}
%		\caption{
%		Scatter plots of mean axial velocity as a function of the horizontal coordinate,
%	        for $\Rey_b=17000, N = 8$ (a) and $\Rey_b=133000, N = 16$ (b), in blue.
%	        Only points at wall distance greater than five
%	        Ekman layer thicknesses are shown.
%		The black dashed lines denote the velocity profile given in equation~\eqref{eq:uzfit}.
%	}
%	        \label{fig:scatter}
%	\end{figure}
%
%	\begin{figure}
%		\centering
%		(a) \includegraphics[width=5.0cm]{Figures/ekman_theta_500.eps} 
%	        (b) \includegraphics[width=5.0cm]{Figures/ekman_theta_3000.eps} \\
%		\includegraphics[width=0.5\textwidth]{Figures/theta_cmap.eps}
%		\caption{Mean axial velocity profiles scaled by the local geostrophic velocity ($U_g$),
%		as a function of wall distance normalised by the local Ekman layer thickness,
%		$\Delta = (\nu/(\Omega \sin \theta))^{1/2}$,
%		at $\Rey_b=17000$, $N=8$ (a), and $\Rey_b=133000$, $N=16$ (b).
%		Profiles along the pipe perimeter are shown in intervals of $7.5^{\circ}$, with exception of $\theta=0^{\circ}$, $\theta=180^{\circ}$.
%		}
%		\label{fig:Uznorm} 
%	\end{figure}
%
%	\begin{figure}
%		\centering
%		\begin{tabular}{ll}
%		\includegraphics[width=6.0cm]{Figures/lambda_rotating_a.eps} &
%		\includegraphics[width=6.0cm]{Figures/lambda_rotating_b.eps} \\
%		(a) & (b) \\
%		\end{tabular}
%		\caption{
%		    Distribution of friction factor as a function of $(N/\Rey_b)^{1/2}$,
%		    for DNS data at $\Rey_b=17000$ ($\bm{+}$), $\Rey_b=44000$ ($\bm{*}$),
%		    $\Rey_b=82500$ ($\bigstar$), $\Rey_b=133000$ ($\blacksquare$).
%		    In panel (a) the solid line denotes the asymptotic prediction for the rapid-rotation regime~\eqref{eq:lambda_as}.
%		    Lines in (b) denote prediction of the interpolation formula~\eqref{eq:lambda_int} 
%		    at $\Rey_b=17000$ (blue), $\Rey_b=44000$ (red),
%                    $\Rey_b=82500$ (orange), $\Rey_b=133000$ (purple).}
%			\label{fig:lambda}
%	\end{figure}
%
%	 
%	\begin{figure}
%		\centering
%		\begin{tabular}{ll}
%		\includegraphics[width=6.0cm]{Figures/kt_lam_ito_a.eps} &
%		\includegraphics[width=6.0cm]{Figures/kt_lam_ito_b.eps} \\
%		(a) & (b) \\
%		\end{tabular}
%		\caption{
%		    Distribution of friction factor (normalised by the non-rotating case value) as a
%		    function of the parameter $K_t = \Rey_b N^2/4$~\citep{ito71},
%		    for DNS data at $\Rey_b=17000$ ($\bm{+}$), $\Rey_b=44000$ ($\bm{*}$),
%		    $\Rey_b=82500$ ($\bigstar$), $\Rey_b=133000$ ($\blacksquare$).
%		    In panel (a) the black line denotes the composite correlation
%		    \eqref{eq:ito_low}+\eqref{eq:ito_high}, and in panel (b)
%		    the power-law fit~\eqref{eq:ming_fit}.
%		}
%			\label{fig:ito}
%	\end{figure}

	\section{Conclusions} \label{sec:conclusions}

\appendix

\section{}

%\label{Appendix}

%\begin{table}
%                \begin{center}
%                        \def~{\hphantom{0}}
%                        \begin{tabular}{cccccccc}
%                                \toprule
%                                $\Rey_b$ & $\Rey_\tau$ & $N$ & $L_z/R$  & $N_z \times N_r \times N_\theta$ & $\lambda \times 10^{-2}$ & Line \\
%                                \midrule
%                                17000 & 669  & 0.5  &  $15$  & $769  \times 97  \times 769$  & 4.963& \textcolor{black}{\rule{0.05\linewidth}{0.75mm}} \\
%                                17000 & 669  & 0.5  &  $30$  & $1537 \times 97  \times 769$  & 4.963& \textcolor{red}{\rule{0.05\linewidth}{0.75mm}} \\
%                                17000 & 669  & 0.5  &  $45$  & $2305 \times 97  \times 769$  & 4.963& \textcolor{blue}{\rule{0.05\linewidth}{0.75mm}} \\
%                                17000 & 670  & 0.5  &  $15$  & $769  \times 193 \times 769$  & 4.977& \textcolor{orange}{\rule{0.05\linewidth}{0.75mm}} \\
%                                17000 & 669  & 0.5  &  $15$  & $769  \times 97  \times 1537$ & 4.966& \textcolor{green}{\rule{0.05\linewidth}{0.75mm}} \\
%                                \bottomrule
%                        \end{tabular}
%                        \caption{
%                                Computational parameters for grid sensitivity study.
%				See table~\ref{tab:runs} for the nomenclature.
%                }
%                                \label{tab:runs_grid}
%                \end{center}
%\end{table}

%\begin{figure}
%                \centering
%                (a) \includegraphics[width=4.cm]{Figures/zplus_azimuth_500.eps}
%                (b) \includegraphics[width=4.cm]{Figures/thetaplus_azimuth_500.eps}
%                (c) \includegraphics[width=4.cm]{Figures/rplus_azimuth_500.eps} \\
%                (d) \includegraphics[width=4.cm]{Figures/zplus_azimuth_3000.eps}
%                (e) \includegraphics[width=4.cm]{Figures/thetaplus_azimuth_3000.eps}
%                (f) \includegraphics[width=4.cm]{Figures/rplus_azimuth_3000.eps} \\
%                \caption{
%                        Polar distribution of the inner-scaled grid spacings,
%                        at $\Rey_b=17000$ (a, b, c), and $\Rey_b=133000$ (d, e, f):
%                        streamwise spacing $\Delta z^+$ (a,d), azimuthal spacing $R^+ \Delta \theta$ (b,e), 
%			and radial spacing at the wall $\Delta r_w ^+$ (c,f).
%                        The color codes correspond to different values of $N$,
%                        as given in table~\ref{tab:runs}.
%                    }
%                        \label{fig:grid_polar}
%\end{figure}

%\begin{figure}
% \centering
% (a) \includegraphics[width=3.cm]{Figures/gridref_meanupsi_Lz.eps}
% (b) \includegraphics[width=3.cm]{Figures/gridref_meanupsi_fine.eps}
% \caption{
%  Comparison of cross-flow streamlines at $\Rey_b = 17000$ and $N=0.5$.
%  The pressure side of the pipe is on the left, and the suction side is on the right
%  of each sub-panel. (a) effects of domain length, (b) effects of grid refinement.
%  The color codes correspond to the different runs of the grid sensitivity study, 
%  as given in table~\ref{tab:runs_grid}.
% }
% \label{fig:Urt_500_grid}
%\end{figure}

%In order to highlight changes in secondary motion structures, if any, we depict the 
%representative cross-flow streamlines for the different runs if the grid sensitivity study in figure \ref{fig:Urt_500_grid}.
%Almost no changes are observed when increasing the pipe length, while increasing the resolution in the azimuthal direction
%shows small difference in the streamlines path towards the pressure side.

%\begin{figure}
% \centering
% (a) \includegraphics[width=5.25cm]{Figures/gridref_cf_Lz.eps}
% (b) \includegraphics[width=5.25cm]{Figures/gridref_cf_fine.eps} \\
% \caption{
% Polar distribution of the local streamwise wall shear stress ($\tau_w$),
% normalised by the reference dynamic pressure $\rho u_b ^2$ at
% $\Rey_b=17000$, and $N=0.5$.
% (a) effects of domain length, (b) effects of grid refinement.
% The color codes correspond to the different runs of the grid sensitivity study,
% as given in table~\ref{tab:runs_grid}.
% }
% \label{fig:Cf_polar_grid}
%\end{figure}
%
%\begin{figure}
%   \centering
%   \begin{tabular}{ll}
%   \includegraphics[width=4.6cm]{Figures/gridref_Lz_uzub_500.eps}  &
%   \includegraphics[width=4.6cm]{Figures/gridref_fine_uzub_500.eps} \\
%   (a) & (b) \\
%   \includegraphics[width=4.6cm]{Figures/gridref_Lz_uzub_500_detail.eps} &
%   \includegraphics[width=4.6cm]{Figures/gridref_fine_uzub_500_detail.eps} \\
%   (c) & (d) \\
%   \end{tabular}
%   \caption{
%   Radial profiles of
%   outer-scaled axial velocity
%   at various azimuthal positions,
%   for flow cases at $\Rey_b=17000$, and $N=0.5$.
%   Only the interval $\theta = [0^{\circ},90^{\circ}]$ is shown, at stations
%   spaced $15^\circ$ apart, with negative values of $r$ signifying profiles
%   taken at $\theta + 180^{\circ}$. (a,c) effects of pipe length, (b,d) effects of grid refinement.
%   The color codes correspond to the different runs of the grid sensitivity study,
%                as given in table~\ref{tab:runs_grid}.
%   }
%   \label{fig:uprof_grid}
%\end{figure}

% \backsection[Supplementary data]{\label{SupMat}Supplementary material and movies are available at ...}

%\backsection[Author contributions]{Authors may include details of the contributions made by each author to the manuscript, for example, ``A.G. and T.F. derived the theory and T.F. and T.D. performed the simulations.  All authors contributed equally to analysing data and reaching conclusions, and in writing the paper.''}

%\bibliographystyle{jfm}
%\bibliography{references.bib}

\end{document}

### 2024-12-17 paper.tex
upload 17 dic 2024

@@
 
+\definecolor{black}{rgb}{0.0, 0.0, 0.0}
 \definecolor{green}{rgb}{0.0, 0.5019607843137255, 0.0}
@@
 \definecolor{purple}{rgb}{0.5019607843137255, 0.0, 0.5019607843137255}
-\definecolor{black}{rgb}{0.0,0.0,0.0}
-\definecolor{magenta}{rgb}{1.0,0.0,1.0}
-\definecolor{blue}{rgb}{0.0,0.0,1.0}
+\definecolor{magenta}{rgb}{1.0, 0.0, 1.0}
+\definecolor{blue}{rgb}{0.0, 0.0, 1.0}
+\definecolor{pink}{rgb}{1.0, 0.75, 0.8}
+\definecolor{violet}{rgb}{0.56, 0.0, 1.0}
+\definecolor{darkgreen}{rgb}{0.0, 0.392, 0.0}
 
@@
 			$\mathbf{F}_c$ is the resultant mean Coriolis force.
-			\textcolor{blue}{The Cartesian coordinates $x_1,x_2$ define positions in the cross-stream plane.}}
+			The Cartesian coordinates $x_1,x_2$ define positions in the cross-stream plane.}
 			\label{fig:sketch} 
@@
 	 			\midrule
-	 			17000 & 508  & 0.0078125 &  $769 \times 97 \times 769$ & 2.862& - \\
-	 			17000 & 512  & 0.015625  &  $769 \times 97 \times 769$ & 2.942& - \\
-	 			17000 & 523  & 0.03125   &  $769 \times 97 \times 769$ & 3.030& \textcolor{green}{\rule{0.05\linewidth}{0.75mm}} \\
-	 			17000 & 538  & 0.0625    &  $769 \times 97 \times 769$ & 3.212& \textcolor{cyan}{\rule{0.05\linewidth}{0.75mm}} \\
-	 			17000 & 566  & 0.125     &  $769 \times 97 \times 769$ & 3.553& \textcolor{orange}{\rule{0.05\linewidth}{0.75mm}} \\
-	 			17000 & 610  & 0.25      &  $769 \times 97 \times 769$ & 4.120& \textcolor{red}{\rule{0.05\linewidth}{0.75mm}} \\
-	 			17000 & 642  & 0.375     &  $769 \times 97 \times 769$ & 4.576& \textcolor{purple}{\rule{0.05\linewidth}{0.75mm}} \\
-	 			17000 & 669  & 0.5       &  $769 \times 97 \times 769$ & 4.962& \textcolor{black}{\rule{0.05\linewidth}{0.75mm}} \\
-	 			17000 & 748  & 1.0       &  $769 \times 97 \times 769$ & 6.208& \textcolor{magenta}{\rule{0.05\linewidth}{0.75mm}} \\
-	 			17000 & 856  & 2.0       &  $769 \times 97 \times 769$ & 8.117& \textcolor{blue}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 508  & 0.0078125 &  $769 \times 97 \times 769$ & 2.862& \textcolor{green}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 512  & 0.015625  &  $769 \times 97 \times 769$ & 2.942& \textcolor{cyan}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 523  & 0.03125   &  $769 \times 97 \times 769$ & 3.030& \textcolor{orange}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 538  & 0.0625    &  $769 \times 97 \times 769$ & 3.212& \textcolor{red}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 566  & 0.125     &  $769 \times 97 \times 769$ & 3.553& \textcolor{purple}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 610  & 0.25      &  $769 \times 97 \times 769$ & 4.120& \textcolor{magenta}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 642  & 0.375     &  $769 \times 97 \times 769$ & 4.576& \textcolor{blue}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 669  & 0.5       &  $769 \times 97 \times 769$ & 4.962& \textcolor{pink}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 748  & 1.0       &  $769 \times 97 \times 769$ & 6.208& \textcolor{violet}{\rule{0.05\linewidth}{0.75mm}} \\
+	 			17000 & 856  & 2.0       &  $769 \times 97 \times 769$ & 8.117& \textcolor{darkgreen}{\rule{0.05\linewidth}{0.75mm}} \\
 
@@
 	 			\midrule
-	 			133000 & 3634  & 0.5  & $4609 \times 328 \times 4609$ & 2.389& \textcolor{black}{\rule{0.05\linewidth}{0.75mm}}\\
+	 			133000 & 3634  & 0.5  & $4609 \times 328 \times 4609$ & 2.389& -\\
 	 			\bottomrule
@@
                         (a) $N = 0.0$,
-                        (b) $N = 0.0.078125$,
+                        (b) $N = 0.0078125$,
                         (c) $N = 0.015625$,
@@
 		(i) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.25_T.png} 
-                (j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_u.png} \\
+                (j) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty0.5_T.png} \\
 		(k) \includegraphics[width=2.cm]{Figures/cross_rotz0_roty1.0_T.png} 
@@
                         (a) $N = 0.0$,
-                        (b) $N = 0.0.078125$,
+                        (b) $N = 0.0.0078125$,
                         (c) $N = 0.015625$,
@@
                         (a) $N = 0.0$,
-                        (b) $N = 0.078125$,
+                        (b) $N = 0.0078125$,
                         (c) $N = 0.015625$,
@@
                         (a) $N = 0.0$,
-			(b) $N = 0.078125$,
+			(b) $N = 0.0078125$,
                         (c) $N = 0.015625$,
@@
 		taken at $\theta + 180^{\circ}$.
-                (a) $N = 0.0.078125$,
+                (a) $N = 0.0078125$,
                 (b) $N = 0.015625$,
@@
                 taken at $\theta + 180^{\circ}$.
-                (a) $N = 0.0.078125$,
+                (a) $N = 0.0078125$,
                 (b) $N = 0.015625$,
@@
 		Only the interval $\theta = [0^{\circ},180^{\circ}]$ is shown.
-    	        (a) $N = 0.0.078125$,
+    	        (a) $N = 0.0078125$,
                 (b) $N = 0.015625$,
@@
                 Only the interval $\theta = [0^{\circ},180^{\circ}]$ is shown.
-                (a) $N = 0.0.078125$,
+                (a) $N = 0.0078125$,
                 (b) $N = 0.015625$,
@@
                 The dashed gray lines depict the compound law-of-the wall
-                $U^+=y^+$, $U^+=\log y^+/0.387 + 4.53$.
+                $U^*=y^*$, $U^*=\log y^*/0.387 + 4.53$.
         }
@@
                 The dashed gray lines depict the compound law-of-the wall
-		$\theta^{+}=y^+$, $\theta^{+}=\log y^+/0.387 + 4.53$.
+		$\theta^{*}=y^*$, $\theta^{*}=\log y^*/0.387 + 4.53$.
         }
@@
                taken at $\theta + 180^{\circ}$.
-               (a) $N = 0.03125$,
-               (b) $N = 0.5$,
-               (c) $N = 2.0$,
-               (d) $N = 8.0$.
-               (e) $N = 0.1$,
-               (f) $N = 0.5$,
-               (g) $N = 2.0$,
-               (h) $N = 16.0$.
+               (a) $N = 0.0078125$,
+               (b) $N = 0.015625$,
+               (c) $N = 0.0315$,
+               (d) $N = 0.0625$,
+               (e) $N = 0.125$
+               (f) $N = 0.25$,
+               (g) $N = 0.375$,
+               (h) $N = 0.5$,
+               (i) $N = 1.0$,
+               (j) $N = 2.0$. 
                The black solid line denotes the mean turbulence kinetic energy profile in the
@@
                taken at $\theta + 180^{\circ}$.
-               (a) $N = 0.03125$,
-               (b) $N = 0.5$,
-               (c) $N = 2.0$,
-               (d) $N = 8.0$.
-               (e) $N = 0.1$,
-               (f) $N = 0.5$,
-               (g) $N = 2.0$,
-               (h) $N = 16.0$.
+               (a) $N = 0.0078125$,
+               (b) $N = 0.015625$,
+               (c) $N = 0.0315$,
+               (d) $N = 0.0625$,
+               (e) $N = 0.125$
+               (f) $N = 0.25$,
+               (g) $N = 0.375$,
+               (h) $N = 0.5$,
+               (i) $N = 1.0$,
+               (j) $N = 2.0$.
 	       The black solid line denotes the Reynolds shear stress profile in the
@@
 %	 
-%	\begin{figure}
-%    	\centering
-%		\begin{tabular}{lll}
-%		\includegraphics[width=4.cm]{Figures/ekman_uz_utheta_500.eps} &
-%		\includegraphics[width=4.cm]{Figures/ekman_angle_500.eps} &
-%		\includegraphics[width=4.cm]{Figures/ekman_spiral_500.eps} \\
-%		(a) & (b) & (c) \\	
-%		\end{tabular}
-%    	\caption{
-%    		Profiles of 
-%		mean axial ($U_z$) and azimuthal ($U_\theta$) velocity
-%		(a), wall-parallel flow angle $\varphi = \tan^{-1} (U_{\theta}/U_z)$ (b) 
-%		and hodograph diagram (c) 
-%		at the polar coordinate $\theta = \pi/2$ (north pole of the pipe).
-%		Data are shown for $\Rey_b=17000$, at various rotation numbers:
-%    		$N = 0.03125$,
-%    		$N = 0.0625$,
-%    		$N = 0.125$,
-%    		$N = 0.25$,
-%    		$N = 0.5$,
-%    		$N = 2.0$,
-%    		$N = 4.0$,
-%    		$N = 8.0$,
-%		see table~\ref{tab:runs} for the color codes.
-%    		The velocity profiles are scaled by the 
-%    		mean centreline axial velocity $U_{0}$.
-%    		The black circles denote the analytical solution 
-%		for a laminar Ekman layer~\citep{greenspan1968}.
-%    	}
-%		\label{fig:Ekman_500}
-%	\end{figure}
-%	 
+	\begin{figure}
+    	\centering
+		\begin{tabular}{lll}
+		\includegraphics[width=4.cm]{Figures/ekman_profsy_roty_500_u.eps} &
+		\includegraphics[width=4.cm]{Figures/ekman_angles_roty_500_u.eps} &
+		\includegraphics[width=4.cm]{Figures/ekman_spiral_roty_500_u.eps} \\
+		(a) & (b) & (c) \\	
+		\end{tabular}
+    	\caption{
+    		Profiles of 
+		mean axial ($U_z$) and azimuthal ($U_\theta$) velocity
+		(a), wall-parallel flow angle $\varphi = \tan^{-1} (U_{\theta}/U_z)$ (b) 
+		and hodograph diagram (c) 
+		at the polar coordinate $\theta = \pi/2$ (north pole of the pipe).
+		Data are shown for $\Rey_b=17000$, at various rotation numbers:
+    		(a) $N = 0.0078125$,
+                (b) $N = 0.015625$,
+                (c) $N = 0.0315$,
+                (d) $N = 0.0625$,
+                (e) $N = 0.125$
+                (f) $N = 0.25$,
+                (g) $N = 0.375$,
+                (h) $N = 0.5$,
+                (i) $N = 1.0$,
+                (j) $N = 2.0$.
+		see table~\ref{tab:runs} for the color codes.
+    		The velocity profiles are scaled by the 
+    		mean centreline axial velocity $U_{0}$.
+    		The black circles denote the analytical solution 
+		for a laminar Ekman layer~\citep{greenspan1968}.
+    	}
+		\label{fig:Ekman_500}
+	\end{figure}
+
+        \begin{figure}
+        \centering
+                \begin{tabular}{ll}
+                \includegraphics[width=5.cm]{Figures/ekman_profsyr_roty_500_T.eps} &
+                \includegraphics[width=5.cm]{Figures/ekman_profsyd_roty_500_T.eps} \\ 
+			(a) & (b) \\
+                \end{tabular}
+        \caption{
+                Profiles of
+		the temperature $\Theta$ plotted at the poles of the pipe
+                as a function of the radial coordinate normalised by the pipe radius (a) and the wall normal coordinate
+                normalised by the local Ekman layer thickness (b).
+                Data are shown for $\Rey_b=17000$, at various rotation numbers:
+                (a) $N = 0.0078125$,
+                (b) $N = 0.015625$,
+                (c) $N = 0.0315$,
+                (d) $N = 0.0625$,
+                (e) $N = 0.125$
+                (f) $N = 0.25$,
+                (g) $N = 0.375$,
+                (h) $N = 0.5$,
+                (i) $N = 1.0$,
+                (j) $N = 2.0$.
+		see table~\ref{tab:runs} for the color codes.
+                The temperature profiles are scaled by the
+                temperature at the center of the pipe $T_{CL}$.
+        }
+                \label{fig:Ekman_T_500}
+        \end{figure}
+
+        \begin{figure}
+        \centering
+                \begin{tabular}{ll}
+                \includegraphics[width=5.cm]{Figures/ekman_profsyr_roty_500_T_alternative.eps} &
+		\includegraphics[width=5.cm]{Figures/ekman_profsyd_roty_500_T_alternative.eps} \\
+                (a) & (b) \\
+                \end{tabular}
+        \caption{
+                Profiles of
+		the temperature $\Theta$ plotted at the poles of the pipe 
+		as a function of the radial coordinate normalised by the pipe radius (a) and the wall normal coordinate 
+		normalised by the local Ekman layer thickness (b).  
+                Data are shown for $\Rey_b=17000$, at various rotation numbers:
+                (a) $N = 0.0078125$,
+                (b) $N = 0.015625$,
+                (c) $N = 0.0315$,
+                (d) $N = 0.0625$,
+                (e) $N = 0.125$
+                (f) $N = 0.25$,
+                (g) $N = 0.375$,
+                (h) $N = 0.5$,
+                (i) $N = 1.0$,
+                (j) $N = 2.0$.
+                see table~\ref{tab:runs} for the color codes.
+                The temperature profiles are scaled by the
+		temperature taken at the edge of the Ekman layer $T_{6\Delta}$.
+        }
+                \label{fig:Ekman_T_6delta_500}
+        \end{figure}
+
+	\begin{figure}
+                \centering
+                \begin{tabular}{lll}
+		\includegraphics[width=4cm]{Figures/ch_azimuth_global_500.eps} &
+		\includegraphics[width=4cm]{Figures/ch_azimuth_local_500.eps} &
+                \includegraphics[width=4cm]{Figures/sra_azimuth_local_500.eps} \\
+		(a) & (b) & (c) \\
+                \end{tabular}
+                \caption{
+			Polar distribution of the ratio of the local Stanton number and the global Stanton number (a), 
+			polar distribution of the local Stanton number (b)  
+			and polar distribution of the local Strong Reynolds Analogy factor (c), at $\Rey_b=17000$.
+                        The color codes correspond to different values of $N$,
+                        as given in table~\ref{tab:runs},
+                        black denoting cases without rotation.
+                        }
+                        \label{fig:Ch__azimuth_polar}
+        \end{figure}
+
+	\begin{figure}
+                \centering
+                (a) \includegraphics[width=5.25cm]{Figures//sra_global_500.eps}
+                (b) \includegraphics[width=5.25cm]{Figures//ch_cf_500.eps} \\
+                \caption{
+			On the left the global Strong Reynolds Analogy factor as function of the rotation number $N$ (a) 
+			and on the right the global Stanton number and friction coefficient as function of the rotation number (b).
+                        }
+                        \label{fig:Ch_Cf}
+        \end{figure}
+
 %	\begin{figure}
@@
 %		at $\Rey_b=17000$, $N=8$ (a), and $\Rey_b=133000$, $N=16$ (b).
-%		Profiles along the pipe perimeter are shown in intervals of $7.5^{\circ}$, with exception of $\theta=0^{\circ}$, $\theta=180^{\circ}$.
+%		Profiles along the pipe perimeter are shown in intervals of $7.5^{\circ}$, 
+%		with exception of $\theta=0^{\circ}$, $\theta=180^{\circ}$.
 %		}
